### 2024-01-08 inst/scripts/exploreNeutralTraits.Rmd
exploring traits fixations

>>>>

Let# s play with adaptive traits

```{r}
population[,traitsid]=0
for(i in 1:z){population[population[,"community"]==i,traitsid[i]]=1}
knitr::kable(aggregate(population[,traitsid],by=list(population[,"community"]),sum))
tstep=2000
repli=50
library(parallel)
neutraltraitsParam$s=c(0,0,1,1)

par(mfrow=c(2,3))
for(rr in 1:2){
for(pth in 1:3){
plot(1,1,ylim=c(0,1),xlim=c(0,1000),pch="n")
sapply(rhodepSBBIB[[rr]][[pth]],function(olo)sapply(1:4,function(tr)lines(olo[,tr],col=tr)))
```
